Using numerical modelling to investigate temperature and wave exposure as drivers

### 2019-10-09 morphology_paper.Rmd
added detail to wave power (exposure) figure caption

```{r wave power map, echo=FALSE, eval= TRUE, fig.cap='\\label{fig:wave power map}Wave power map'}

>>>>

```{r wave power map, echo=FALSE, eval= TRUE, fig.cap='\\label{fig:wave power map}The total coastal wave exposure of the Cape Peninsula is given in terms of wave energy (kW per meter wave crest length. Annual total (A), summer (B), winter (C), spring (D) and autumn (D).'}
